Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-05-08 tex/manuscript.tex
final draft for submission

\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{textcomp}
\usepackage{array}
\usepackage{xtab}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{nameref}
\usepackage{epstopdf}
\newcolumntype{m}[1]{D{.}{~}{#1}}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}
\newcommand{\breakfill}{\dotfill\newline\penalty0\hbox{}\nobreak\dotfill}
\makeatletter
\def\ttl@useclass#1#2{%
  \@ifstar
    {\ttl@labelfalse\@dblarg{#1{#2}}}
    {\ttl@labelfalse\@dblarg{#1{#2}}}}
\makeatother
\usepackage[counterclockwise]{rotating}
\graphicspath{{figures/}}
\extrafloats{50}

@@

	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2018] remains currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionidae [non-focal]: Entiminae [non-focal] -- higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}). 
	A recent phylogenetic revision of the \textit{Minyomerus} [JF2015] recognized a total of 17 described species, distributed throughout the desert and plains regions of North America \citep{jansen2015}.

@@

	\textit{Minyomerus} [JF2018] belongs to the broad-nosed weevils, subfamily Entiminae [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
	The adults are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales ("setae") arranged in rows on the elytral intervals. Their length can range from 2.8 mm to 6.0 mm \citep{jansen2015}.
	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibrissae that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.

@@

	\begin{enumerate} [itemsep=-0.4em]
		\item Taehe intercoxal process of the prosternum is medially divided into two halves, with the procoxae apparently contiguous in most.
		\item The elytral humeri are rounded rather than angled and protruding.
		\item The profemora are not dilated and lack spines.
		\item The protibiae are ventrally excavated by a longitudinal groove or concavity.
		\item A distinct scrobe is present and directed ventrad of the eye, with a more or less apparent tooth formed by an overhang of the dorsal margin.
	\end{enumerate}

	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional, undescribed species. These are known to us only from limited numbers of specimens, yet are well circumscribed by -- i.e., intensionally included in \citep{fp2009} -- the recent generic delimitation of \textit{Minyomerus} [JF2015].
	In other words, the addition of these new species \emph{has not} required altering the intensional, property-based definition of the genus-level concept as circumscribed in \citet{jansen2015} (see \textbf{\nameref{sec:results}}). Our RCC--5 alignments (see \textbf{\nameref{sec:alignments}}) reflect this genus-level concept congruence while also showing which classificatory and phylogenetic structures have changed (Figs.~\ref{fig:align1}-\ref{fig:align3}).
	The precise use of the taxonomic concept labels in accordance with either [JF2015] or [JF2018] is meant to minimize the creation of new taxonomic concept labels (to counter label "inflation"; see \citet{fp2009}), while reflecting explicitly \emph{which} taxonomic concepts we consider as relevantly new and unique to the present study.

	Here we describe the four newly found species of \textit{Minyomerus} [JF2018] and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2018], based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} [JF2018] is given, along with an updated species checklist.
	Where possible, we make note of host-plant records, and briefly discuss the geographic distributions of the herein described species.
	A more extensive discussion of the habits, distribution, and delimitation of the \textit{Minyomerus} [JF2015] and all of its constituent species is provided in \citep{jansen2015}.

@@

	\subsection*{Morphological analysis}\label{ssec:morph} 
		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
		The terminology for exterior morphology is in general accordance with \citet{torre1989}.
		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
			\citet{thompson1992} for tibial apices and abdominal segments;
			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.

@@

\section*{To Do}
	\begin{enumerate}[itemsep=-0.4em]
		\item Submit names to zoobank.
		\item Upload matrix data to dryad.
		\item Upload pre-prints to bioR{\textchi}iv.
		\item Make sure all Checklist nomenclatural references are included -- Green 1920, Casey 1888, Pierce 1909, etc.
	\end{enumerate}

\newpage
\bibliography{references} 
%just references in windows, use references.bib in linux

>>>>

\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{textcomp}
\usepackage{array}
\usepackage{xtab}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{nameref}
%\usepackage{epstopdf}
\newcolumntype{m}[1]{D{.}{~}{#1}}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}
\newcommand{\breakfill}{\dotfill\newline\penalty0\hbox{}\nobreak\dotfill}
\makeatletter
\def\ttl@useclass#1#2{%
  \@ifstar
    {\ttl@labelfalse\@dblarg{#1{#2}}}
    {\ttl@labelfalse\@dblarg{#1{#2}}}}
\makeatother
\usepackage[counterclockwise]{rotating}
\graphicspath{{figures/}}
\extrafloats{50}

@@

	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2018] remains currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionidae [non-focal]: Entiminae [non-focal] -- higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}). 
	A recent phylogenetic revision of the genus \textit{Minyomerus} [JF2015] recognized a total of 17 described species, distributed throughout the desert and plains regions of North America \citep{jansen2015}.

@@

	\textit{Minyomerus} [JF2018] belongs to the broad-nosed weevils, subfamily Entiminae [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
	The adults are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales (``setae'') arranged in rows on the elytral intervals. Their body length can range from 2.8 mm to 6.0 mm \citep{jansen2015}.
	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibrissae that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.

@@

	\begin{enumerate} [itemsep=-0.4em]
		\item The intercoxal process of the prosternum is medially divided into two halves, with the procoxae apparently contiguous in most.
		\item The elytral humeri are rounded rather than angled and protruding.
		\item The profemora are not dilated and lack spines.
		\item The protibiae are ventrally excavated by a longitudinal groove or concavity.
		\item A distinct scrobe is present and directed ventrad of the eye, with a more or less apparent tooth formed by an overhang of the dorsal margin.
	\end{enumerate}

	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional, undescribed species.
	These are known to us only from limited numbers of specimens, yet are well circumscribed by -- i.e., intensionally included in (see \citealt{fp2009}) -- the recent generic delimitation of \textit{Minyomerus} [JF2015].
	In other words, the addition of these new species \emph{has not} required altering the intensional, property-based definition of the genus-level concept as circumscribed in \citet{jansen2015} (see \textbf{\nameref{sec:results}}).
	Our RCC--5 alignments (see \textbf{\nameref{sec:alignments}}) reflect this genus-level concept congruence while also showing which classificatory and phylogenetic structures have changed (Figs.~\ref{fig:align1}-\ref{fig:align3}).
	The precise use of the taxonomic concept labels in accordance with either [JF2015] or [JF2018] is meant to minimize the creation of new taxonomic concept labels (to counter label ``inflation''; see \citet{fp2009}), while reflecting explicitly \emph{which} taxonomic concepts we consider as relevantly new and unique to the present study.

	Here we describe the four newly found species of \textit{Minyomerus} [JF2018] and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2018], based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} [JF2018] is given, along with an updated species checklist.
	Where possible, we make note of host-plant records, and briefly discuss the geographic distributions of the herein described species.
	A more extensive discussion of the habits, distribution, and delimitation of the genus \textit{Minyomerus} [JF2015] and all of its constituent species is provided in \citet{jansen2015}.

@@

	\subsection*{Morphological analysis}\label{ssec:morph} 
		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
		The terminology for exterior morphology is in general accordance with \citet{torre1989}.
		Additional morphological terms specific to broad-nosed weevils (Entiminae [non-focal]) were used as follows:
			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
			\citet{thompson1992} for tibial apices and abdominal segments;
			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.

@@

\bibliography{references}
\nocite{*}
